A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-11 doc/popl2013/example.tex
Minor edits

In addition to privileges, functions can also specify {\em coherence}
on regions.  Coherence specifies what updates the function may
see from other functions using the same region.  If not otherwise
specified, coherence defaults to {\em exclusive}, meaning the
function must appear to execute in program order.  Line 14 shows
an example of {\tt atomic}, a relaxed coherence mode requiring
that operations to {\tt rn} and {\tt rg} appear atomic relative
to other functions using those regions.  The most relaxed coherence
mode is {\tt simult}; simultaneous coherence allows concurrent access 
to the region by all functions with simultaneous coherence on the region.

>>>>

In addition to privileges, functions can also specify {\em coherence}
on regions.  Coherence specifies what updates the function may
see from other functions using the same region.  If not otherwise
specified, coherence defaults to {\em exclusive}, meaning the
function must appear to execute in program order.  Line 14 shows
an example of {\tt atomic}, a relaxed coherence mode requiring
that operations to {\tt rn} and {\tt rg} appear atomic relative
to other functions using those regions.  The most relaxed coherence
mode is {\tt simult}; simultaneous coherence allows concurrent access 
to the region by all functions that are using the region
in a simultaneous mode.  The interaction between tasks using the same
region with different coherence
modes is formalized in Section~\ref{sec:coherence}.

### 2012-07-11 doc/popl2013/intro.tex
Minor edits

In Legion data is organized in a hierarchy of {\em regions}
and subregions while computation is organized in a hierarchy of {\em
tasks} and subtasks operating on regions.  Regions and tasks interact
through a static system of {\em region privileges} specifying 
operations a task may perform on a region argument (read,
write, or reduce) and  {\em region coherence} annotations that
express what other tasks may do concurrently with
the region (exclusive, atomic, or simultaneous).  We prove the
soundness of the privileges and coherence system and use these two
results to prove a third result: if two {\em siblings} (tasks that
have the same immediate parent task) $t_1$ and $t_2$ are 
{\em non-interfering} (have no ordering requirements for correctness), 
then the any descendant of $t_1$ in the task hierarchy is non-interfering
with any descendant of $t_2$.  This theorem is the basis for correct distributed
task scheduling in a Legion implementation, which is crucial for
performance; a centralized scheduler would be a bottleneck
because of the huge latencies involved in communicating in the target
class of machines.

>>>>

In Legion data is organized in a hierarchy of {\em regions}
and subregions while computation is organized in a hierarchy of {\em
tasks} and subtasks operating on regions.  Regions and tasks interact
through a static system of {\em region privileges} specifying 
operations a task may perform on a region argument (read,
write, or reduce) and  {\em region coherence} annotations that
express what other tasks may do concurrently with
the region (exclusive, atomic, or simultaneous).  We prove the
soundness of the privileges and coherence system and use these two
results to prove a third result: if two {\em siblings} (tasks that
have the same immediate parent task) $t_1$ and $t_2$ are 
{\em non-interfering} (have no ordering requirements for correctness), 
then the any descendant of $t_1$ in the task hierarchy is non-interfering
with any descendant of $t_2$.  This theorem is the basis for correct distributed
task scheduling in a Legion implementation, which is crucial for
performance; a centralized scheduler would be a bottleneck
because of the large communication latencies in the target
class of machines.
